Supplement to Example Manuscript Template for a Data Analysis Project

### 2025-04-18 code/analysis-code/statistical-analysis.qmd
Part 5 V2

```
```{r}
# Publication Quality table
# Step 1: Create survival object (if not already created)
# Replace with your actual survival time and event columns
# surv_obj <- Surv(time = mydata_filtered$survival_months, event = mydata_filtered$death_flag)

@@

```
```{r}
#Publication-ready Table 
# Step 1: Recode the race variable (if not already done)
mydata_filtered <- mydata_filtered %>%
  mutate(race = factor(race, levels = c(
    "White", "Black", "Asian or Pacific Islander", "American Indian/Alaska Native"
  )))

@@

```
```{r}
#Publication-ready table

>>>>

```{r}
# Publication Quality table
# Step 1: Create survival object (if not already created)
# Replace with your actual survival time and event columns
# surv_obj <- Surv(time = mydata_filtered$survival_months, event = mydata_filtered$death_flag)

@@

```{r}
#Publication-ready Table 
# Step 1: Recode the race variable (if not already done)
mydata_filtered <- mydata_filtered %>%
  mutate(race = factor(race, levels = c(
    "White", "Black", "Asian or Pacific Islander", "American Indian/Alaska Native"
  )))

@@

```{r}
#Publication-ready table

### 2025-04-18 products/manuscript/supplement/Supplementary-Material.qmd
Part 5 V2

---
title: "Supplement to Example Manuscript Template for a Data Analysis Project"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
```

@@

### Directory Structure Overview

ZUBER-MADA-project/
│
├── data/
│   ├── raw-data/           # Contains the original input datasets (raw files)
│   └── processed-data/     # Contains the cleaned and transformed datasets
│
├── code/
│   ├── processing-code/    # Data cleaning scripts
│   ├── eda-code/           # Exploratory data analysis scripts
│   └── analysis-code/      # Statistical modeling and prediction
│
├── results/
│   ├── edatables/          # Exploratory summary tables
│   ├── edafigures/         # Exploratory plots
│   ├── tables/             # Model results tables
│   ├── figures/            # Model-related figures
│   └── output/             # Rendered final outputs (PDF/HTML)
│
├── products/
│   ├── manuscript/         # Manuscript and supplementary files
│   ├── poster/             # Poster material (if applicable)
│   └── slides/             # Presentation slides (if applicable)
│
├── assets/                 # Bibliography and citation style files
└── README.md               # Project overview and general usage instructions

@@

## LASSO Cox Model Performance at 12 Months
To assess the discriminatory ability of the LASSO Cox regression model, we evaluated model performance at 12 months post-diagnosis. The linear predictor (risk score) was used to generate a receiver operating characteristic (ROC) curve, and area under the curve (AUC) was calculated. Additionally, we computed a confusion matrix using a default threshold of 0 for classification.

@tbl-lasso-auc. Model discrimination at 12 months, measured by area under the ROC curve (AUC). The LASSO Cox model achieved a moderate discriminative ability with an AUC of 0.664.
```{r}
#| label: tbl-lasso-auc
#| tbl-cap: "AUC for the LASSO Cox model at 12-month survival prediction."
#| echo: FALSE
paste("AUC at 12 months:", round(auc_val, 3))

@tbl-lasso-cm. Confusion matrix at 12 months using a classification threshold of 0. The model achieved high sensitivity (87.8%) but low specificity (25.7%), indicating it was better at correctly identifying deaths than survivals at this time point.
```{r}
#| label: tbl-lasso-cm
#| tbl-cap: "Confusion matrix for LASSO Cox model predicting 12-month mortality."
#| echo: FALSE
conf_matrix

# Discussion

Any additional discussion regarding the supplementary material/findings.

These papers [@mckay2020; @mckay2020a] are good examples of papers published using a fully reproducible setup similar to the one shown in this template.

# References

>>>>

---
title: "Supplement to Example Manuscript Template for a Data Analysis Project"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
---

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)

@@

# Directory Structure Overview

### 📁 Directory Structure Overview

```
ZUBER-MADA-project/
├── data/
│   ├── raw-data/           # Original input datasets (raw files)
│   └── processed-data/     # Cleaned and transformed datasets
│
├── code/
│   ├── processing-code/    # Data cleaning scripts
│   ├── eda-code/           # Exploratory data analysis scripts
│   └── analysis-code/      # Statistical modeling and prediction
│
├── results/
│   ├── edatables/          # Exploratory summary tables
│   ├── edafigures/         # Exploratory plots
│   ├── tables/             # Model results tables
│   ├── figures/            # Model-related figures
│   └── output/             # Rendered final outputs (PDF/HTML)
│
├── products/
│   ├── manuscript/         # Manuscript and supplementary files
│   ├── poster/             # Poster material (if applicable)
│   └── slides/             # Presentation slides (if applicable)
│
├── assets/                 # Bibliography and citation style files
└── README.md               # Project overview and general usage instructions
```

@@
